Refinements for open automata

### 2022-07-15 2021-Refinement/paper/refinementarticle.tex
examples

\begin{document}
%
\title{Refinements for open automata}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
Rabéa Ameur-Boulifa\inst{1}\orcidID{0000-0002-2471-8012} \and
Quentin Corradi\inst{2}\orcidID{} \and
Ludovic Henrio \inst{2}\orcidID{0000-0001-7137-3523} \and
Eric Madelaine \inst{3}\orcidID{0000-0002-5552-5993}}
%
\authorrunning{Rab\'ea Ameur-Boulifa et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris, France
\email{first.last@telecom-paris.fr}\\
\and
Universit\'e Lyon, EnsL, UCBL, CNRS, Inria,  LIP France\\
\email{first.last@ens-lyon.fr}
 \and
INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA,  Sophia Antipolis, France
\email{first.last@inria.fr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%\TODO{ The abstract should briefly summarize the contents of the paper in 150--250 words.}

@@

\TODO{Entete : rabea}

@@

\begin{figure}[h]
 \centering
   \includegraphics[width=.5\textwidth]{Figures/counter.pdf}\hfill 
   \includegraphics[width=.3\textwidth]{Figures/compose_count_db.pdf}
   \caption{(Left) Open Automaton of \texttt{counter} process.  Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart. (Right) Open Automaton of the composition \texttt{database}[\texttt{counter/cnt}].\label{Fig:counter}}
\end{figure}
In Fig. \ref{Fig:counter} (right) we present the composition \texttt{database}[\texttt{counter/cnt}] of the two open automata \texttt{database} and \texttt{counter}. Each state of the composite consists of a state of \texttt{database} together with a state of \texttt{counter}. The composed automaton  takes over  the same steps as the   \texttt{database} automaton but it also includes new steps,  indicating the change of states for the setting of timer.

\subsection{Relations between open automata}
A relation (bisimulation, refinement, etc.) between OA requires to compare their states. To do so we will suppose that the variables of the two OA are disjoint (a renaming of variables may have to be applied before comparing OA states).
\begin{definition}[Relation on OA configurations] Suppose $V_1$ and $V_2$ are disjoint.
A relation on configurations of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
\end{definition}
%\TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat... +1}
The idea is that two states are related depending on the state of the automaton, i.e. if the variables of the OA verify a certain formula. 
In other words, for each pair of states, a boolean formula that may refer to the  variables of each of the two OA states whether the two states are related or not.
Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\).

@@

A  bisimulation relation  relates pair of states and ensures that any behaviour of one automaton can be performed by the other one while staying in relation. We informally explain here the symbolic nature of the bisimulation and the related complexity of its definition. The presence of holes in fact raises no strong difficulty here.
Consider the two following simple OA.

@@

We would like these two OA to be considered bisimilar. Both can input any $\beta(x)$ input on their hole and stores the value of $x$, emitting $\alpha(x)$ along the transition.
The different is the way $x$ is stored. We can then define a configuration relation $R$ such that $R(s,s_2)$ is true and $R(t,t_2)$ holds when $z\geq 0$ and $y=z$, while $R(t',t_2)$ holds when $z< 0$ and $y=-z$. This illustrates relation on configuration, but also allows us to realise that bisimulation is a bit more complex than in the classical case. Indeed, we need two transitions on the left OA to simulate a single transition on the right one. We should check that these two transitions cover all the cases accepted by te right hand side OA, and of course that destination states are in relation. Formally, fh-bisimulation is defined \cite{fhbisim} as follows

@@

We define now a simulation between OA that have the same set of holes. This relation thus focuses on the simulation of transitions and uses the previous definition to prevent the refined automaton from nondeterministically reaching states that introduce deadlocks in a scenario planned without deadlock in the specification.
\begin{definition}[Hole-equal simulation]
Consider two OA with identical set of holes:  \(\OAg[1]\) and \(\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold: 
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
\noindent\begin{multline*}
\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[10pt]
		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \nwedge\\[2pt]
		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\
\hspace{5em} \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \nwedge\\[12pt]
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}\right)
	\end{array} 
%\\
%	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
\end{multline*}
\item[(3)] $R$ is  is preserved along identical transitions of \(A_1\) and \(A_2\).
\end{definition}

@@

\begin{example} 
To illustrate the refinement simulation of open automata, consider a variation on the \texttt{database} automaton of Fig. \ref{Fig:RefineOA}. We suppose that on more concrete level, in addition to querying and updating the data base,  a backup copy of it may also be made.
\end{example}
\begin{figure}[!tb]
 \centering
   \includegraphics[width=.9\textwidth]{Figures/databaseRefine.pdf}
   \caption{The refined Open Automaton of the automaton of Fig.\ref{Fig:SpecOA}.  Two other actions,  in addition to  \texttt{qry} and \texttt{upd},  \texttt{back} representing a request to make a backup copy and    \texttt{cpy} is used to reflect the actual operation of copying. \label{Fig:RefineOA}}
\end{figure}

@@

\begin{figure}[h]
 \centering
   \includegraphics[width=.6\textwidth]{Figures/composeRefined.pdf}
   \caption{The refined Open Automaton composed with the counter \label{Fig:ComposeRefine}}
\end{figure}

@@

@@

The next  theorem states that if two automata are in refinement relation and the same automata is placed in the same hole of the two automata, then the refinement is preserved. This is the first step toward proving that
 refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
The second part, i.e. proving that placing in the same context two OA in refinement, we obtain two OA in refinement is left for future works.
%
%
%The composition of $A_1$ and $A_3$ is a refinement of the composition of $A_2$ and $A_3$ provided $A_1$ is a refinement of $A_2$ and the hole in which we are composing inside $A_1$ and $A_2$ is tracked by the refinement relation.

@@

The bisimulation relation that we consider is the one that makes $A_1$ and $A_2$ bisimilar, complemented with identity of configurations for $A_3$.
The proof relies on the fact that, by construction, all transitions of the composed automaton $A_1\subst{A_3}{k}$ are specified by open transitions of $A_1$. For the transitions that do not involve hole $k$, the transition of $A_1\subst{A_3}{k}$ is the same and simulation between $A_1$ and $A_2$ allows us to conclude directly. If the hole $k$ is involved the considered relation  implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because Post are deterministic.

\TODO{[RABEA] example : composition and refinement}

@@

\TODO{[RABEA] proof}
Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ we have the following:

\begin{multline*}
\bigforall \mpar{s_1, s_{2p}} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_{2p}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2p}{}{2p}{2p}} \in \fOT{s_1} \times \fOT{s_{2p}} \\ 
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
 V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2p} \wedge \alpha_1 = \alpha_{2p} 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pj} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_{2p} \land \bigwedge_\subbox{j \in J'_{2p} } \beta_{2pj} = \beta_{1xj}\land g_{1 x}\land
 R_{12}\mpar{s'_{1 x}, s'_{2p}}\psubst{\psi_{1 x} \uplus \psi_{2p}}}
\end{multline*}

>>>>

\begin{document}
%
\title{Refinements for open automata}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
Rabéa Ameur-Boulifa\inst{1}\orcidID{0000-0002-2471-8012} \and
Quentin Corradi\inst{2}\orcidID{0000-0003-4218-3987} \and
Ludovic Henrio \inst{2}\orcidID{0000-0001-7137-3523} \and
Eric Madelaine \inst{3}\orcidID{0000-0002-5552-5993}}
%
\authorrunning{Rab\'ea Ameur-Boulifa et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris, France
\email{first.last@telecom-paris.fr}\\
\and
Universit\'e Lyon, EnsL, UCBL, CNRS, Inria,  LIP, France\\
\email{first.last@ens-lyon.fr}
 \and
INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA,  France
\email{first.last@inria.fr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%\TODO{ The abstract should briefly summarize the contents of the paper in 150--250 words.}

@@

@@

\begin{figure}[h]
 \centering
   \includegraphics[width=.55\textwidth]{Figures/counter.pdf}\hfill 
   \includegraphics[width=.35\textwidth]{Figures/compose_count_db.pdf}
   \caption{(Left) Open Automaton of \texttt{counter} process.  Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart. (Right) Open Automaton of the composition \texttt{database}[\texttt{counter/cnt}].\label{Fig:counter}}
\end{figure}

\begin{example}
In Fig. \ref{Fig:counter} (right) we present the composition \texttt{database}[\texttt{counter/cnt}] of the two open automata \texttt{database} and \texttt{counter}. Each state of the composite consists of a state of \texttt{database} together with a state of \texttt{counter}. The composed automaton  takes over  the same steps as the   \texttt{database} automaton but it also includes new steps,  indicating the change of states for the setting of timer.  Note how restricting the composition to a synchronisation of actions (of the encompassing automaton and  of the hole) corresponds to imposing of a change in states. This example also shows how value passing works: the time limit of the counter is set by the parameter \texttt{n} carried by  the \texttt{set} action.
\end{example}

\subsection{Relations between open automata}
A relation (bisimulation, refinement, etc.) between OA requires to compare their states. To do so we will suppose that the variables of the two OA are disjoint (a renaming of variables may have to be applied before comparing OA states).
\begin{definition}[Relation on OA configurations] Suppose $V_1$ and $V_2$ are disjoint.
A relation on configurations of two OA \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
\end{definition}
%\TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat... +1}
The idea is that two states are related depending on the state of the automaton, i.e. if the variables of the OA verify a certain formula. 
In other words, for each pair of states, a boolean formula that may refer to the  variables of each of the two OA states whether the two states are related or not.
Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\).

@@

A  bisimulation relation  relates pair of states and ensures that any behaviour of one automaton can be performed by the other one while staying in relation. We informally explain here the symbolic nature of the bisimulation and the related complexity of its definition. The presence of holes in fact raises no strong difficulty here.
Consider the two following simple OA:

@@

We would like these two OA to be considered bisimilar. Both can input any $\beta(x)$ input on their hole and stores the value of $x$, emitting $\alpha(x)$ along the transition.
The different is the way $x$ is stored. We can then define a configuration relation $R$ such that $R(s,s_2)$ is true and $R(t,t_2)$ holds when $z\geq 0$ and $y=z$, while $R(t',t_2)$ holds when $z< 0$ and $y=-z$. This illustrates relation on configuration, but also allows us to realise that bisimulation is a bit more complex than in the classical case. Indeed, we need two transitions on the left OA to simulate a single transition on the right one. We should check that these two transitions cover all the cases accepted by te right hand side OA, and of course that destination states are in relation. Formally, fh-bisimulation is defined \cite{fhbisim} as follows:

@@

We define now a simulation between OA that have the same set of holes. This relation thus focuses on the simulation of transitions and uses the previous definition to prevent the refined automaton from non-deterministically reaching states that introduce deadlocks in a scenario planned without deadlock in the specification.
\begin{definition}[Hole-equal simulation]
Consider two OA with identical set of holes:  \(\OAg[1]\) and \(\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold: 
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
\noindent\begin{multline*}
\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[10pt]
		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \nwedge\\[2pt]
		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\
\hspace{5em} \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \nwedge\\[12pt]
			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}\right)
	\end{array} 
%\\
%	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
\end{multline*}
\item[(3)] $R$ is  is preserved along identical transitions of \(A_1\) and \(A_2\).
\end{definition}

@@

\begin{example} 
To illustrate the refinement simulation of open automata, consider a variation on the \texttt{database}.  We suppose that on more concrete level, in addition to querying and updating the data base,  a backup copy of it may also be made. The behaviour of the concrete database is given by 
an open automaton  depicted in Fig. \ref{Fig:RefineOA}. 
\end{example}
\begin{figure}[!tb]
 \centering
   \includegraphics[width=.9\textwidth]{Figures/databaseRefine.pdf}
   \caption{Another variant of the \texttt{database} process.  Two other actions,  in addition to  \texttt{qry} and \texttt{upd},  \texttt{back} representing a request to make a backup copy and    \texttt{cpy} are used to reflect the actual operation of copying. \label{Fig:RefineOA}}
\end{figure}

@@

@@

\begin{example} It is easy to see the  open automaton of Fig.~\ref{Fig:RefineOA} is a refinement the open automaton of Fig.~\ref{Fig:SpecOA} according to this definition.
\end{example}

@@

The next  theorem states that if two automata are in refinement relation and the same automaton is placed in the same hole of the two automata, then the refinement is preserved. This is the first step toward proving that
 refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
The second part, i.e. proving that placing in the same context two open automata in refinement, we obtain two open automata in refinement is left for future works.
%
%
%The composition of $A_1$ and $A_3$ is a refinement of the composition of $A_2$ and $A_3$ provided $A_1$ is a refinement of $A_2$ and the hole in which we are composing inside $A_1$ and $A_2$ is tracked by the refinement relation.

@@

The bisimulation relation that we consider is the one that makes $A_1$ and $A_2$ bisimilar, complemented with identity of configurations for $A_3$.
The proof relies on the fact that, by construction, all transitions of the composed automaton $A_1\subst{A_3}{k}$ are specified by open transitions of $A_1$. For the transitions that do not involve hole $k$, the transition of $A_1\subst{A_3}{k}$ is the same and simulation between $A_1$ and $A_2$ allows us to conclude directly. If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
\begin{example} The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata depicted in Fig.~\ref{Fig:ComposeRefine}.
\end{example}

\begin{figure}[h]
 \centering
   \includegraphics[width=.6\textwidth]{Figures/composeRefined.pdf}
   \caption{Open automata resulting from the composition of the  refined  \texttt{database} and the \texttt{counter} \label{Fig:ComposeRefine}}
\end{figure}

@@

\newpage
\TODO{[RABEA] proof}
Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
\begin{align*}
\OTx{1}{}{1}{1} \in \fOT{s_1}
\end{align*}
there exists an indexed family of OTs originating from $s_{2p}$: 
\begin{align*}
\mpar{\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{x \in X_p} 
\end{align*}
such that $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
		\end{array}}} 
\end{multline*}	
According to the refinement  relation between   $A_2$ and $A_3$, we know the following is satisfied, in particular for  the set $(t_{2pxy})^{x\in X_p}$:
\begin{multline*}
\bigforall \mpar{s_{2p}, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_{2px}, t_3} = \mpar{\OTx{2px}{}{2px}{2px}, \OTx{3}{}{3}{3}} \in \fOT{s_{2p}} \times \fOT{s_3} \\ 
\bigsymb{\bigexists} 
\mpar{t_{2pxy} = \OTx{2px}{y}{2pxy}{2pxy} \in \fOT{s_{2p}}}^{y \in Y},
V_2 \uplus V_3\uplus \biguplus_{y\in Y}\fvars{t_{2pxy}} \uplus \fvars{t_3} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{23}\mpar{s_{2p}, s_3} \wedge 	g_{2px}\wedge g_3 \wedge \alpha_{2px}= \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2pj} = \beta_{3j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
\bigsymb{\bigwedge_{y\in Y}}
\mpar{
\alpha_{2px}=\alpha_{2p xy}  \land J'_{2pxy}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2pxyj}\land g_{2p xy}\land
 R_{23}\mpar{s'_{2p xy}, s'_3}\psubst{\psi_{2p xy} \uplus \psi_3}}\\
\end{multline*}
Yet according to the refinement  relation between  $A_1$ and $A_2$ the following is satisfied, in particular over the family of transitions in $Y$:
\begin{multline*}
\bigforall \mpar{s_1, s_{2p}} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_{2pxy}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2pxy}{}{2pxy}{2pxy}} \in \fOT{s_1} \times \fOT{s_{2p}} \\ 
\bigsymb{\bigexists} 
\mpar{t_{1z} = \OTx{1}{z}{1z}{1z} \in \fOT{s_1}}^{z \in Z},
 V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2pxy} \wedge \alpha_1 = \alpha_{2pxy} 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pxyj} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{z\in Z}}
\mpar{
\alpha_1=\alpha_{1 z}  \land J'_{1z}= J'_{2pxy} \land \bigwedge_\subbox{j \in J'_{2pxy} } \beta_{2pxyj} = \beta_{1zj}\land g_{1 z}\land
 R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}}
\end{multline*}

From previous formulas we get:

\begin{multline*}
\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2pxy} \wedge \alpha_1 = \alpha_{2pxy}} \wedge \mpar{ R_{23}\mpar{s_{2p}, s_3} \wedge 	g_{2px}\wedge g_3 \wedge \alpha_{2px}= \alpha_3 } 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{z\in Z}}
\mpar{
\alpha_1=\alpha_{1 z}  \land J'_{1z}= J'_{2pxy} \land \bigwedge_\subbox{j \in J'_{2pxy} } \beta_{2pxyj} = \beta_{1zj}\land g_{1 z}\land
 R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}} \wedge \\\bigsymb{\bigwedge_{y\in Y}}
\mpar{
\alpha_{2px}=\alpha_{2p xy}  \land J'_{2pxy}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2pxyj}\land g_{2p xy}\land
 R_{23}\mpar{s'_{2p xy}, s'_3}\psubst{\psi_{2p xy} \uplus \psi_3}}
\end{multline*}

--------------------------------------------------
